
\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french,english]{babel}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{lipsum}

% Mise en page
\geometry{margin=2.5cm}
\setstretch{1.3}

% Style des titres
\titleformat{\section}{\Large\bfseries}{\thesection.}{0.5em}{}

% En-tête
\title{\textbf{Checkpoint – Web Development Basics}}
\author{Yassine Kalthoum \\ MSC: Software Engineering}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\section{How does the web work?}

The web works through communication between clients (web browsers) and servers using the Internet.\\[0.3cm]
Here’s the process step-by-step:

\begin{enumerate}
    \item I type a URL (\texttt{www.gomycode.com}) into the browser.
    \item The browser sends a request to a DNS server to find the IP address of that website.
    \item Once it finds the IP, the browser sends an HTTP/HTTPS request to the web server.
    \item The server processes the request (for example, accessing a database) and sends back a response — usually HTML, CSS, and JavaScript files.
    \item The browser interprets these files and displays the web page.
\end{enumerate}

\noindent
\textbf{In conclusion:}\\
Browser $\rightarrow$ Internet $\rightarrow$ Server $\rightarrow$ Response $\rightarrow$ Display Web Page

\newpage

\section{What do you need to be a web developer?}

To become a web developer, you need both technical skills and tools.

\subsection*{Core Skills}
\begin{itemize}
    \item HTML → structure of web pages
    \item CSS → design and layout
    \item JavaScript → interactivity and logic
\end{itemize}

\subsection*{Advanced Skills (for professional work)}
\begin{itemize}
    \item Frontend frameworks: React, Angular, or Vue.js
    \item Backend: Node.js, PHP, Python (Django/Flask), or Java (Spring)
    \item Databases: MySQL, MongoDB, PostgreSQL
    \item APIs: REST or GraphQL
    \item Version Control: Git \& GitHub
    \item Deployment Tools: Docker, Cloud services (AWS, Azure, Google Cloud)
\end{itemize}

\subsection*{Tools}
\begin{itemize}
    \item A code editor (like VS Code / Notepad++)
    \item A browser (like Chrome) for testing
    \item Command line (Terminal) for running scripts
    \item Internet connection
\end{itemize}

\newpage

\section{Why did you choose to learn web development?}

Here are common (and strong) reasons that I can adapt to my own motivation:

\begin{itemize}
    \item \textbf{Career opportunities:} Web development offers high-demand jobs and freelancing options.
    \item \textbf{It’s everywhere:} Every company needs a website or web app.
    \item \textbf{Creativity \& logic:} I can create real products — from simple pages to complex applications.
    \item \textbf{Constant learning:} The web evolves fast, so I always learn new tools and technologies.
    \item \textbf{Freedom:} I can work remotely, build personal projects, and start my own business.
\end{itemize}

\end{document}
